---
title: "Why degree"
output: html_document
---

When confronted with the question "How would this degree help fulfill your aspirations?", I thought nothing talks louder than data. So I collected some data and did this analysis.  

#Data Collection
- I searched for jobs named "data scientist", and checked out the most relevant 120 results.
- Then I selected jobs with specific requirements about degrees.
- And I also selected jobs with different job level to see the trend.

#Overview of data
```{r read data, echo = FALSE}
raw_data <- read.csv("Why degree.csv", sep = ";", header = TRUE)
head(raw_data)
```
Then we check out how many of them requires a Master degree.  
```{r overview, echo = FALSE}
library(ggplot2)
library(grid)
p1 <- ggplot(raw_data)+geom_bar(aes(x = Minimum.Requirement ,fill = Minimum.Requirement ))+labs(title = "Overview of the job requirements.")+labs(y = "Num. of certain requirement")
p2 <-ggplot(raw_data)+geom_bar(aes(x = factor(1), fill = Minimum.Requirement))+labs(title = "Pie chart of different requirements")+labs(x = " ")+labs(y = " ")+coord_polar(theta = "y")
grid.newpage()
pushViewport(viewport(layout = grid.layout(2, 1)))
vplayout <-  function(x,y){
  viewport(layout.pos.row = x, layout.pos.col = y)
}
print(p1, vp = vplayout(1,1))
print(p2, vp = vplayout(2,1))
```

Here we can see that half of the jobs do not require a master degree. Then why should I need one?  

#Why should I need a master degree
##A master degree is a license to senior jobs
Unlike the previous analysis, more senior jobs require a master degree

```{r analysis about seniro jobs, echo = FALSE}
p1 <- ggplot(subset(raw_data, Job.Level == "Junior"))+geom_bar(aes(x = Minimum.Requirement ,fill = Minimum.Requirement ))+labs(title = "Junior jobs")+labs(y = "Num. of requirements")
p2 <-ggplot(subset(raw_data, Job.Level == "Junior"))+geom_bar(aes(x = factor(1), fill = Minimum.Requirement))+labs(x = " ")+labs(y = " ")+coord_polar(theta = "y")
p3 <- ggplot(subset(raw_data, Job.Level == "Senior"))+geom_bar(aes(x = Minimum.Requirement ,fill = Minimum.Requirement ))+labs(title = "Senior jobs")+labs(y = "Num. of requirements")
p4 <-ggplot(subset(raw_data, Job.Level == "Senior"))+geom_bar(aes(x = factor(1), fill = Minimum.Requirement))+labs(x = " ")+labs(y = " ")+coord_polar(theta = "y")
grid.newpage()
pushViewport(viewport(layout = grid.layout(2, 2)))
print(p1, vp = vplayout(1,1))
print(p3, vp = vplayout(1,2))
print(p2, vp = vplayout(2,1))
print(p4, vp = vplayout(2,2))
```

The total number of jobs from different job level are different. So it's better to compare them via pie chart.   
And we can observe that a larger part of senior jobs require a master degree.     

##A master degree is a license to Fortune 500 companies
Things are more obvious when talking about jobs in a Fortune 500 company.
```{r analysis about big name companies, echo = FALSE}
p1 <- ggplot(subset(raw_data, Fortune500 == 0))+geom_bar(aes(x = Minimum.Requirement ,fill = Minimum.Requirement ))+labs(title = "Oidinary companies")+labs(y = "Num. of requirements")
p2 <-ggplot(subset(raw_data, Fortune500 == 0))+geom_bar(aes(x = factor(1), fill = Minimum.Requirement))+labs(x = " ")+labs(y = " ")+coord_polar(theta = "y")
p3 <- ggplot(subset(raw_data, Fortune500 == 1))+geom_bar(aes(x = Minimum.Requirement ,fill = Minimum.Requirement ))+labs(title = "Fortune 500 companies")+labs(y = "Num. of requirements")
p4 <-ggplot(subset(raw_data, Fortune500 == 1))+geom_bar(aes(x = factor(1), fill = Minimum.Requirement))+labs(x = " ")+labs(y = " ")+coord_polar(theta = "y")
grid.newpage()
pushViewport(viewport(layout = grid.layout(2, 2)))
print(p1, vp = vplayout(1,1))
print(p3, vp = vplayout(1,2))
print(p2, vp = vplayout(2,1))
print(p4, vp = vplayout(2,2))
```

When we focus on the pie chart, we can see a larger part of jobs offered by a Fortune 500 company requires a master degree.   

##Sum up
In a word, a master degree can give me more opportunities as being an outstaning data scientist. Espeically a master degree of business analytics offered by MIT.

